### 2025-09-20 paper/sec/authoring-workflow.tex
New interpretation agent figure.
Figure.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{fig/entire-workflow}
    \caption{Workflow}\label{fig:architecture}
\end{figure}

Figure~\ref{fig:architecture} shows the overall architecture of the system. The author initially provides the
text and accompanying data. The \SuggestionAgent analyses the input and identifies candidate fragments of
natural language which could be replaced by Fluid expressions. The user highlightes a fragment of interest,
which is then sent to the \InterpretationAgent, which generates a corresponding candidate expression.
Internally the \InterpretationAgent uses a compiler-in-the-loop validation process to ensure the expression is
well-formed. The user is then able to accept the expression (in which case it is incorporated into the
program) or reject and leave the text uninterpreted.

@@

\begin{figure}[h]
    \centering
    \begin{tcolorbox}[colback=gray!10, colframe=gray!50, boxrule=0.5pt, arc=2pt,
        left=6pt, right=6pt, top=4pt, bottom=4pt]
        \VerbatimInput[fontsize=\small, formatcom=\normalfont]{../system-prompt/system-prompt.txt}
    \end{tcolorbox}
    \vspace{-0.5em}
    \caption{System Prompt defined for the Authoring Assistant}
    \label{fig:system-prompt}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{fig/interpretation-agent}
    \caption{Human-in-the-Loop \InterpretationAgent workflow (Author intervention states in grey)}
    \label{fig:interpretation-agent}
\end{figure}

Figure~\ref{fig:interpretation-agent} shows the overall architecture of the \InterpretationAgent. The author
initially provides the text and accompanying data. The \SuggestionAgent analyses the input and identifies
candidate fragments of natural language which could be replaced by Fluid expressions. The user highlightes a
fragment of interest, which is then sent to the \InterpretationAgent, which generates a corresponding
candidate expression. Internally the \InterpretationAgent uses a compiler-in-the-loop validation process to
ensure the expression is well-formed. The user is then able to accept the expression (in which case it is
incorporated into the program) or reject and leave the text uninterpreted.

@@

\begin{figure}[h]
    \centering
    \begin{tcolorbox}[colback=gray!10, colframe=gray!50, boxrule=0.5pt, arc=2pt,
        left=6pt, right=6pt, top=4pt, bottom=4pt]
        \VerbatimInput[fontsize=\small, formatcom=\normalfont]{../system-prompt/interpretation-agent/system-prompt.txt}
    \end{tcolorbox}
    \vspace{-0.5em}
    \caption{System Prompt defined for the Authoring Assistant}
    \label{fig:system-prompt}
\end{figure}
